GxHash: A High-Throughput, Non-Cryptographic Hashing Algorithm Leveraging Modern CPU Capabilities

### 2023-11-07 article/article.tex
Fix typo in article
Fix confusion with laning in article

Let's define \( n_g = \lfloor {n_b}/{k_b} \rfloor \) as the number of whole groups of \( k_b \) message blocks. \\
For each lane we compute an intermediate hash, \( H_i \), as follows:

@@

\paragraph{Random Blobs}\leavevmode\\

@@

\subsubsection{Compiler Dependencies} 
The Temporal Construction presented in this paper is implemented for GxHash by declaring each lane with its own variable. While it worked at the time of writing (rustc 1.68.0), it is in the end the compiler's responsibility to decide how many registers to use. We cannot exclude that in another context (different version, different language/compiler, ...) the compiler will undo the ILP we tried to implicitly introduce. This could be countered by writing the algorithm directly in assembly code, at the cost of complexity.

\subsection{Future Work}
Despite the outstanding benchmark results, we think there are still many possible paths for research and improvement. Here is a non-exhaustive list:
\begin{itemize}
    \item Leverage larger SIMD intrinsics, such as Intel AVX-512 or ARM SVE2.
    \item Make use of compiler hints to improve branching predictions.
    \item Benchmark in more test suite to further assess the distribution and avalanche properties.
    \item Analyze security properties.
    \item Rewrite the algorithm in assembly code or a language that is more explicit about registers.
    \item Introduce more than one stage of laning. For instance 16 lanes, then 8 lanes, then 4 lanes, and finally 2 lanes, to leverage ILP as much as possible.
    \item Organize processing loop to result in even less bytecode to be generated, favoring inlining opportunities.
    \item Fine-tune the finalization stage to find the perfect balance between performance and avalanche effect.
\end{itemize}

>>>>

Let's define \( n_g = \lfloor {n_b}/{k_b} \rfloor \) as the number of whole groups of \( k_b \) message blocks. \\
For each group we compute an intermediate hash, \( H_i \), as follows:

@@

@@

\subsubsection{Compiler Dependencies} 
The Temporal Construction presented in this paper is implemented for GxHash by declaring at temporary variable on each group iteration, assuming that the compilers understands that most of each iteration can be parallelized. While it worked at the time of writing (rustc 1.68.0), it is in the end the compiler's responsibility to decide how many registers to use. We cannot exclude that in another context (different version, different language/compiler, ...) the compiler will undo the ILP we tried to implicitly introduce. This could be countered by writing the algorithm directly in assembly code, at the cost of complexity.

\subsection{Future Work}
Despite the outstanding benchmark results, we think there are still many possible paths for research and improvement. Here is a non-exhaustive list:
\begin{itemize}
    \item Leverage larger SIMD intrinsics, such as Intel AVX-512 or ARM SVE2.
    \item Make use of compiler hints to improve branching predictions.
    \item Benchmark in more test suite to further assess the distribution and avalanche properties.
    \item Analyze security properties.
    \item Rewrite the algorithm in assembly code or a language that is more explicit about registers.
    \item Organize processing loop to result in even less bytecode to be generated, favoring inlining opportunities.
    \item Fine-tune the finalization stage to find the perfect balance between performance and avalanche effect.
\end{itemize}
